### 2017-04-06 Manuscript/ms.tex
Adding description of posteror predictive checks

The posterior distribution can be written as:
\begin{equation}
aaaaaaah
\end{equation}
Samples from this distribution were generated using Hamiltonian Monte Carlo (CITATIONS) implemented in the rstan package for R. 
Within stan, the solution to the differential equation model was approximated with an Euler scheme with a time step of 1 day.

>>>>

Samples from the posterior distribution were generated using Hamiltonian Monte Carlo (CITATIONS) implemented in the rstan package for R. 
We ran 3 chains with different starting values for 10,000 iterations each, discarding the first 5,000 as burn-in.
Within stan, the solution to the differential equation model was approximated with an Euler scheme with a time step of 1 day.

We evaluate the goodness-of-fit of the estimated mosquito abundance time series through the use of posterior predictive checks \cite{Gelman1996,Gelman2003}.
Specifically, for each iteration, $i$, of MCMC, we sample
\begin{equation}
q^{rep(i)}_t \sim \text{NegBin}(\phi^{(i)}_q \tau_t V^{(i)}_{Nt}, \eta^{(i)}_q)
\end{equation}
and compute
\begin{equation}
p_t = P(q^{rep}_t > q_t) = \frac{1}{M}\sum I(q^{rep(i)}_t > q_t).
\end{equation}
If the reconstructed mosquito trajectories are a good fit for the observed mosquito trap counts, then we would expect the time series $p_t$ to be random in time (CITATION?).
Any systematic trends in $p_t$ indicate lack-of-fit.

In addition to looking at weekly comparisons, we also develop posterior checks to compare the temporal variability and correlation structures of the observed and expected time series.
To test whether the estimated time series capture the seasonal features of the observed mosquito data, we compute the posterior auto-correlation function of the replicate data:
\begin{equation}
R^{rep(i)}(l) = \text{corr}(q^{rep(i)}_t, q^{rep(i)}_{t-l}),
\end{equation}
for lags ranging from 1 to 55 weeks.
We also compute posterior distributions of $\min(q^{rep}_t)$ , $\max(q^{rep}_t)$, and $\sigma(q^{rep}_t - q^{rep}_{t-1})$ as measures of the smoothness of the modeled process.
